### 2012-09-03 inst/examples/figure3.Rmd
updated figure3 for a replicate run

theme_publish <- theme_set(theme_bw(14))
theme_publish <- 
  theme_update(axis.line=theme_blank(),
        axis.text.y=theme_blank(),
        legend.position=c(.9,.1),
        panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
        plot.background=theme_blank(), legend.title=theme_blank())

@@

``` {r }
xmin <- 0
xmax <- 1.5 * K
grid_n <- 100
````

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r runall}
lvl <- 0.5
det <- scenario(0.001, 0.00, 0.00)
g   <- scenario(lvl, 0, 0)
m   <- scenario(0, lvl, 0)
i   <- scenario(0, 0, lvl)
````

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1],
               growth = g$D[,1], measurement = m$D[,1], implementation = i$D[,1]), 
               id = "stock")

>>>>

theme_publish <- theme_set(theme_bw(14))
theme_publish <- 
  theme_update(legend.key = theme_blank(),legend.position=c(.9,.1),
        panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
        plot.background=theme_blank(), legend.title=theme_blank())

@@

``` {r }
xmin <- 0
xmax <- 1.5 * K
grid_n <- 200
````

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r runall}
lvl <- 0.5
low <- scenario(0.1, 0.1, 0.1)
det <- scenario(0.001, 0.00, 0.00)
g   <- scenario(lvl, 0, 0)
m   <- scenario(0, lvl, 0)
i   <- scenario(0, 0, lvl)
````

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], all_low = low$D[,1],
               growth = g$D[,1], measurement = m$D[,1], implementation = i$D[,1]), 
               id = "stock")
